\sysfull

### 2017-08-09 paper/evaluation.tex
Kiwan's compiler text revised (added questions for Kiwan to respond)

\begin{table}[t]
	\centering
	\footnotesize
	\begin{tabular}{|c|c|c|c|c|c|c|c|}
		\hline
		{} & \multicolumn{2}{l|}{{PVAR Size (Byte)}} & \multicolumn{2}{l|}{{\# Tasks}} & \multicolumn{2}{l|}{{\# Paging Code}} \\
		\hline
		Nickname & Hand & Comp. & Hand & Comp. & Hand & Comp.\\
		\hline\hline
		Bitcount & 22 & 22 & 10 & 15 & 81 & 93 \\
		Cold chain & 3492 & 3242 & 12 & 9 & 92 & 123\\
		Cuckoo & 282 & 288 & 15 & 6 & 90 & 76\\
		RSA & 332 & 250 & 20 & 27 & 130 & 296\\
		AR & 166 & 218 & 11 & 6 & 112 & 333\\
		Sort & 104 & 104 & 4 & 2 & 70 & 23\\
		\hline
	\end{tabular}
	\caption{Comparison between compiler-generated code (Comp.) and hand-written \sys code (Hand).}
\label{table:compiler_result}
\end{table}

We start with evaluating the efficiency of a \sys compiler. Table~\ref{table:compiler_result} shows
the difference in size of protected variable (PVAR), number of tasks, and number of inserted paging call in the code between hand-written \sys code
and compiler-generated \sys code. All three values are better to be small. On average, compiler-generated
code is only worse by 0.3\% in the size of protected variable. Regarding the number of tasks, compiler-generated code
is better by roughly 16\%. The result indicate compiler is selecting boundaries better than programmer manually doing it.
However, compiler should insert paging code conservatively when it {\em may} access protected variable, due to limitation of
pointer alias. Thus, it results in compiler introducing 48\% more paging code than programmer-written code. The resulting run time
difference is summarized in Figure~\ref{}. The performance is worse than programmer-written \sys code
in overall, meaning the programmer should try to write code manually if performance is critical; otherwise compiler can be
used to simplify the programmability.

We also evaluated the compile time for automatic task generation. The result are in Table~\ref{table:compile_time}.
Most of the compile time was due to pointer aliasing. We could not compile DFT application since it was using
builtins for math functions that weren't provided by Clang MSP430 backend.

\begin{table}[t]
	\centering
	\footnotesize
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		Bitcount & Cold chain & Cuckoo & RSA & AR & Sort \\
		\hline\hline
		3 & 2 & 6 & 86 & 34 & > 1 \\
		\hline
	\end{tabular}
	\caption{Compile time in seconds.}
\label{table:compile_time}
\end{table}

>>>>

\begin{table}[t]
	\centering
	\footnotesize
	\begin{tabular}{|c|c|c|c|c|c|c|c|}
		\hline
		{} & \multicolumn{2}{l|}{{PVAR size (Byte)}} & \multicolumn{2}{c|}{{No. tasks}} & \multicolumn{2}{c|}{{No. paging code}} \\
		\hline
		Nickname & Hand & Comp. & Hand & Comp. & Hand & Comp. \\
		\hline\hline
		Bitcount & 22 & 22 & 10 & 15 & 81 & 93 \\
		Cold chain & 3492 & 3242 & 12 & 9 & 92 & 123 \\
		Cuckoo & 282 & 288 & 15 & 6 & 90 & 76 \\
		RSA & 332 & 250 & 20 & 27 & 130 & 296 \\
		AR & 166 & 218 & 11 & 6 & 112 & 333 \\
		Sort & 104 & 104 & 4 & 2 & 70 & 23 \\
		\hline
	\end{tabular}
	\caption{Comparison between compiler-generated \sys code (Comp.) and hand-written \sys code (Hand).}
\label{table:compiler_result}
\end{table}

We start with evaluating the efficiency of a \sys compiler. Table~\ref{table:compiler_result} shows the difference in the number of protected variables (PVAR), number of tasks, and number of inserted paging calls in the code between (i) hand-written \sys and (ii) compiler-generated \sys code. On average, compiler-generated code is only worse by 0.3\% in the number of protected variables. Regarding the number of tasks, compiler-generated code is better by roughly 16\%. The result indicate that \sys compiler is selecting boundaries better than the programmer doing it manually. However, \sys compiler should insert paging code conservatively when it {\em may} access protected variables, due to limitation of pointer alias. Thus, it results in \sys compiler introducing 48\% more paging code than programmer-written code (the results on run time for various \sys code versions is provide in Section~\ref{}). The performance is worse than programmer-written \sys code in overall, meaning the programmer should structure the code manually if the performance is critical; otherwise compiler can be used to simplify the programmability.

Additionally, we evaluated the compile time for automatic task generation per application\footnote{We could not compile DFT application since it was using built-ins for C math functions (i.e. \texttt{rand()}, \texttt{sinf()}, \texttt{cosf()}) that were not provided by the Clang MSP430 back-end.}. The result are given in Table~\ref{table:compile_time}. Most of the compile time was due to pointer aliasing.\todo{Comment on: whether these times are good or bad; why there is such a difference in time between all applications; how many runs you performed; what PC/OS you used to run the code; how the result was measured; why results are rounded (there are no decimals in your result); what is "Clang MSP430 back-end"}{Kiwan}

\begin{table}[t]
	\centering
	\footnotesize
	\begin{tabular}{|c|c|c|c|c|c|}
		\hline
		Bitcount & Cold chain & Cuckoo & RSA & AR & Sort \\
		\hline\hline
		3 & 2 & 6 & 86 & 34 & > 1 \\
		\hline
	\end{tabular}
	\caption{\sys compile time per application (seconds).}
\label{table:compile_time}
\end{table}
